### 2020-06-28 Report/aws_325ghz_study.tex
updated minor changes in sec9/10

On basis of the weighting functions of 183\,GHz, three specifications for
325\,GHz channels were suggested. A channel specific simple regression was
tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
The advantage of this approach is that for each 183\,GHz the cloud adjustment
can be quantified simply through a polynomial fit between the the cloud impact
in 183\,GHz channel of concern and brightness temperature differences between
183\,GHz and 325\,GHz. A similar regression scheme based on 229\,GHz was also
examined, but gave poor results. One drawback of the simple correction scheme
is its channel specific approach, which cannot benefit from the other 325\,GHz
channels available. In order to effectively use information from all 325\,GHz
channels, we suggested a machine learning based approach for cloud correction.
We used QRNN (Quantile Regression Neural Network) to to correct the cloud
impact in each 183\,GHz channel using measurements from all available channels
of 325\,GHz. All three options of 325\,GHz were evaluated, and the performance
was comparable. For some channels, interestingly, the spread of errors was
narrower than the noise of the target 183\,GHz channel. Another advantage of
using QRNN is that the cloud free values are predicted at different quantile
levels, which helps in quantifying the case-specific uncertainty estimate. A
similar QRNN model with 229\,GHz gave poor results. No critical dependency to
the 325\,GHz receiver noise temperature was observed.

@@

The cloud correction analysis did not give a clear value on the relative merit
of the suggested channel options and also the measurements' degree of freedom
(DoF) was assessed based on the performed simulations. The DoF can be seen as a
measure of the effective number of channels. The DoF analysis gave further
support for selecting 325\,GHz in favour of 229\,GHz. The DoF of the 325\,GHz
options is higher or equal to the 229\,GHz one already in clear-sky conditions,
while for cloud conditions 325\,GHz consistently gives two additional degrees
of freedom. Some additional 325\,GHz channel versions were considered in the DoF
analysis.

With 325\,GHz as a better option confirmed, the next step is to establish
requirements for these channels. The study considered this question to some
extent. The cloud correction simulations gave no clear constraints on the
requirements, while the DoF analysis at least gave some indications. By
comparison to the NE$\Delta$D requirements for ICI and DoF values derived, it
is suggested to set threshold, target and breakthrough for the 325\,GHz
receiver noise temperature to 2400, 1800 and 1200\,K, respectively. Regarding
number, position and widths of channels, the differences between considered
options are relatively small and at this point it seems reasonable to let
technical considerations guide the basic selection between having three or four
channels. Later, when the technical constraints (such as the IF range
available) are better known an updated assessment should be performed to set
the final channel values.

@@

\subsubsection{Fascod}
\label{sec:fascod}
%
The Fascod dataset \citep{anderson1986afgl} was used to represent different
climate zones in overview calculations. The dataset consists of profiles of
pressure, temperature and volume mixing ratio profiles of various atmospheric
gases. Five climatoligies were used: tropical (TRO), mid-latitude summer (MLS),
mid-latitude winter (MLW), sub-arctic summer (SAS), and sub-arctic winter
(SAW). No hydrometeors were included in simulations involving Fascod.

@@

Since in this study, the cases with cloud impact are extremely important, we used ``clear-sky thinning'' to improve the representation of the cloudy cases in the dataset. Thinned dataset is a subset of the full dataset with 50\% of the clear-sky cases removed (cloud impact $<$ 0.2\,K) The size of the thinned dataset is different for each channel.

@@

A statistical comparison of the simulations to actual ATMS data, for channels
16-22 at nadir (zenith angle = $180^{\degree}$), is shown in
Fig.~\ref{fig:pdf:c16-22}. For the comparison, the daytime ATMS observations
were selected as CloudSat operates only during the day part of the orbit since
2011. For the channels around 183\,GHz, the ATMS characteristics are not fully
simulated. The ATMS channel widths are considered, but as AWS is only covering
the lower wing of the 183\,GHz transition the upper sideband of ATMS is not
included.

@@

In the intermediate region, the simulations have a lower occurrence rate. The
impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
which is not reflected in the simulations, but this is not sufficient to
explain the deviation. As this region is well covered in the simulations
reported in Fig.~7 of \citet{eriksson:towar:20}, the deviation of concern is
presumably also a consequence of the neglected antenna pattern. In this study,
this transitional region is of high interest. For this reason, the PDF for a
50\% random rejection of cases with an insignificant cloud impact is also
shown. This PDF gives a fair match in the intermediate region (but gives an
even higher over-representation at more strong cloud impacts). This smaller
dataset will be considered in parallel below, to ensure that no fraction of the
``cloudy'' cases is not underrepresented in the results.

@@

\subsubsection{Training}
%  
\label{sec:qrnn:training}
\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{quantile_loss.png}
	\caption{The mean quantile loss with different configurations of layer width and hidden layers ($n_h$). Here QRNN is trained to predict clear-sky values for AWS-34 using four channels option of 325\,GHz}
	\label{fig:quantile_loss}
\end{figure}
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz
channels using TBs measurements from all available channels of 325\,GHz. A
separate QRNN is used for each of the 183\,GHz channels. For example, to
predict clear-sky TBs from AWS-34, the training data is measurements from all
channels of 325\,GHz and measurements from the 183\,GHz to be predicted. We
assess the performance of the scheme using both three channel and four channel
options of 325\,GHz. Two suggestions for three channel option are described in
Sec.~\ref{sec:channel:configurations}, and both have been used to train QRNN
separately. Thus, for each channel of 183\,GHz, we have a set of three
predictions: one from four channel option, and two from the old and new
configurations of the three channel option. Further in the text, the old and
new three channel configurations are labelled as "three-a" and "three-b".

To develop the QRNN scheme, we use the same dataset as in the
simple scheme . Out of 125\,000 simulations, 90\% are used to train the model,
while the rest 10\% is used to evaluate the model's performance during
training. Presently we train QRNN for only nadir sensor viewing angle and the
receiver noise $T_r$ = 1200\,K. In the training process, noise is added to the
input according to Eq.~\ref{eq:noise}, every time the training data are exposed
to the model. This ensures that the model is exposed to a new dataset on every
iteration. Before training, the input data is normalized with mean and standard
deviation.

@@

\subsection{Prediction accuracy}
%
We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset. Noise is added to each simulation to mimic a new measurement dataset.

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
		uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
		corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
		corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
		corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\
		\hline
	\end{tabular}
	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}. The labels "three-a", "three-b" correspond to the old and new suggestions of three channels options of 325\,GHz, and the label "four" represents the four channels option.}
	\label{tab:qrnn:C34}
\end{table}

@@

In an analogy between the results from the simple correction scheme and QRNN, we perform a similar error distribution analysis as in Section~\ref{sec:simple}. Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using three (three-b) and four channel options of 325\,GHz. Measurements with cases with $Tb2 - Tb1 > -15$\,K are assumed to be too-cloudy and are filtered out. Here $Tb1$ denotes TBs from AWS-34 and and $Tb2$ is the paired counterpart from 325\,GHz, i.e., AWS-42.  Both the three channels and four channels QRNN models are successful in predicting the clear-sky noise-free value for AWS-34, and the resulting error distribution is symmetric. The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}. The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''. For AWS-34, average deviation in the predictions from all three QRNN models are comparable.  The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.32), however the predictions have relatively symmetric error distributions as reflected by the low skewness values. Among the three set of predictions, option three-b has the most symmetric error distribution but with a relatively large spread. Predictions from option four have the lowest standard deviation (0.620\,K), which is interestingly smaller than the standard deviation of noise (0.641\,K). Though, all three options of 325\,GHz provide a full coverage to the hydrometer impact in AWS-34, predictions from four channel option have slightly better accuracy.

@@

To inspect if the predictions follow a normal distribution we evaluate the
length of confidence intervals from the median.
Figure~\ref{fig:prediction_uncertainty} shows the prediction uncertainty in
AWS-34 (four channel option). The uncertainty with respect to the median for
1000 randomly selected cases is shown. The red line represents the uncertainty
in a hypothetical Gaussian distribution of $270\pm0.62$\,K. If the underlying
distribution is Gaussian, the prediction uncertainty should be symmetric around
the median, and the uncertainties should be equally spaced for $1\sigma$,
$2\sigma$ and so on. The predictions from our QRNN model seem to be symmetric
around the median for the 94\% confidence interval ($\pm 2 \sigma$). The figure
also shows that the uncertainties for all 1000 random cases are concentrated
along a narrow width, thus suggesting that the case to case variability of the
uncertainty is low. A similar uncertainty quantification for other 183\,GHz
channels also gives similar results.

@@

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise                      & -0.001 & 0.451 &              0.020 &      - \\
		uncorrected                & -1.343 & 5.908 &             -7.484 &      - \\
		corrected (AWS-4X)         &  0.008 & 1.514 &             -4.085 &      3.678 \\
		corrected (four channel)   & -0.011 & 0.878 &             -3.030 &      4.930 \\
		\hline
	\end{tabular}
	\caption{Statistics for the error distributions of AWS-32 shown in Figure~\ref{fig:qrnn_C32_C4X:deviations}. The QRNN model is trained with measurements from AWS-4X and AWS-32.}
	\label{tab:qrnn:C32:C4X}
\end{table} 
We also tested the QRNN model to predict cloud-free TBs by using measurements
from AWS-4X and AWS-32 as input. In this case, we trained QRNN with
measurements from AWS-32 and AWS-4X, to predict the clear-sky cloud free TBs
for AWS-32. The model was trained as described in
Section~\ref{sec:qrnn:training}, but slightly better training results were
obtained with width as 256 neurons. Other structural and training parameters
remain unchanged.

@@

\section{Sensitivity to different $T_r$}
\label{sec:tr}
%
In the previous section, we presented the results from QRNN trained using the
three suggestions of 325\,GHz proposed in
section~\ref{sec:channel:configurations}. The receiver noise ($T_r$) was
assumed to be 1200\,K for all cases. In this section, we explore the
sensitivity of QRNN to a higher receiver noise. The QRNN training is repeated
for all three suggestions of 325\,GHz, but with $T_r$ = 1800\,K and $T_r$ =
2400\,K. QRNN is trained with identical structural and training parameters as
described earlier. Tables showing the statistics for error distributions for
each channel are provided. Table~\ref{tab:qrnn:C32:Trec:1800} -
Table~\ref{tab:qrnn:C36:Trec:1800} show the statistics for AWS-32, AWS-33,
AWS-34, AWS-35 and AWS-36 respectively, when $T_r$ = 1800\,K. Similarly
Table~\ref{tab:qrnn:C32:Trec:2400} - Table~\ref{tab:qrnn:C36:Trec:2400} show
the statistics when $T_r$ = 2400\,K.

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      & -0.001 & 0.451 &              0.020 &      - \\
	uncorrected                & -1.342 & 5.908 &             -7.479 &      - \\
	corrected (three-a) 	   & -0.009 & 0.893 &             -3.092 &      4.990 \\
    corrected (three-b) 	   &  0.009 & 0.888 &             -3.197 &      4.902 \\	
	corrected (four channel)   &  0.006 & 0.860 &             -2.943 &      4.954 \\
		\hline
	\end{tabular}
	\caption{Error statistics for AWS-32, when the model is trained with $T_r$ = 1800\,K. The definitions of "three-a", "three-b" and "four" are same as described in Table~\ref{tab:qrnn:C34} }
	\label{tab:qrnn:C32:Trec:1800}
\end{table}

@@

%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.002 & 0.454 &              0.003 &      - \\
uncorrected                 & -1.343 & 5.907 &             -7.483 &      - \\
corrected (three-a)  		& -0.017 & 0.877 &             -3.381 &      4.934 \\
corrected (three-b)  		& -0.015 & 0.882 &             -3.177 &      4.974 \\
corrected (four channel)    &  0.028 & 0.876 &             -3.638 &      4.978 \\
		\hline
	\end{tabular}
	\caption{ Error statistics for AWS-32, when the model is trained with $T_r$ = 2400\,K. The definitions of "three-a", "three-b" and "four" are same as described in Table~\ref{tab:qrnn:C34}  }
	\label{tab:qrnn:C32:Trec:2400}
\end{table}

@@

As example, Fig~\ref{fig:DoF:clear:1200K} shows the ratio of
$\Lambda/S_\Lambda$ with respect to the eigenvalue index for clear-sky cases.
The DoF below is an interpolation between the last index having a ratio above
one and next index.

@@

At this point we got feedback from Omnisys that also channel option 3b is
technically challenging. In short, it is significantly more difficult to
implement a 3\,GHz wide channel at an IF of 3.3\,GHz (AWS-42) than compared to
at 6.5\,GHz (AWS-41). To decrease the ratio between channel widths and centre
IF, a third three channel option was formulated (Table~\ref{tab:chs:3c}) that
is below denoted as three c. This option uses the same IF range as the
previously suggested ones.

@@

\subsection{Impact of extending the IF range}
%
As a basic investigation of the impact of changing the width of the IF range, a
version of the four channel option was considered, denoted as four-b. It was
modified to cover 0.7 to 9.0 GHz (instead of 0.7 to 8.0 GHz). To focus on the
extension, only the edge channels were changed. That is, the revised AWS-41 and AWS-43
have bandwidth of 3.8 and 0.9\,GHz, respectively. The DoFs obtained for four-b
are found in Table~\ref{tab:DoF:4b}.

As expected a slight improvement of the DoF can be seen for four-b. The
exception ``all'' and $T_r=2400$\,K, again likely an indication on some noise
in the DoFs coming out of the analysis.

That is, a broader IF range should give slightly better performance. If a
broader IF range is feasible, the position and width of all channels should be
revised, but this is out of the scope of this study and anyhow hardly motivated
before it is known more exactly to what extent the IF range can be extended.

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
      &	325\,GHz & \multicolumn{3}{c}{DoF}   \\
      &	option &  $T_r = 1200 $\,K &   $T_r = 1800 $\,K &   $T_r = 2400$\,K \\
      \hline
      all &	four   &              8.2 &              7.8 &              6.2 \\
      & four-a   &              8.3 &              8.0   &              6.1 \\

      \hline
      clear  &	four  &                7.0 &              6.0 &              4.9 \\
      &   four-a &                7.0 &              6.4 &              4.9 \\

      \hline	
      cloudy &	four  &              8.7 &              8.5 &              8.3 \\
      &   four-a &              8.8 &              8.6 &              8.4 \\
      \hline
\end{tabular}
\caption{The degrees of freedom for channel option four-b. Values for option
  four are repeated from Tables~\ref{tab:DoF:all}-\ref{tab:DoF:clear}. }
\label{tab:DoF:4b}
\end{table}
\section{Discussion}

@@

\subsubsection{Performance of QRNN}
In section~\ref{sec:qrnn} we use QRNN as a method for cloud correction based on
325\,GHz data. Measurements from all 325\,GHz channels and the 183\,GHz channel
to be predicted are used to train the QRNN model.

@@

For AWS-32, the QRNN trained with 325\,GHz is only partially successful in
reducing the impact of hydrometeors. The resulting error distributions have
significantly lower spread than the measurements, but are still negatively
skewed. Among the three combinations of 325\,GHz, the four channel option has
slightly better performance. Since 325\,GHz cannot provide a full coverage for
hydrometeor impact in AWS-32, QRNN cannot learn to predict cloud free values
for instances which lie outside the area of coverage. In order to compare the
229\,GHz channel with 325\,GHz, QRNN was also trained with AWS-4X to predict
cloud free AWS-32 TBs. The performance of QRNN trained with AWS-4X is worse
than training with 325\,GHz. The spread of error distributions is 1.5 times
more than obtained with four channels option of 325\,GHz.

>>>>

On basis of the relative humidity (RH) weighting functions of 183\,GHz, three specifications for 325\,GHz channels were suggested. A channel specific simple regression was tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
The advantage of this approach is that for each 183\,GHz the cloud adjustment
can be quantified simply through a polynomial fit between the the cloud impact
in 183\,GHz channel of concern and brightness temperature differences between
183\,GHz and 325\,GHz. A similar regression scheme based on 229\,GHz was also
examined, but gave poor results. One drawback of the simple correction scheme
is it's channel specific approach, which cannot benefit from the other 325\,GHz
channels available. In order to effectively use information from all 325\,GHz
channels, we suggested a machine learning based approach for cloud correction.
We used QRNN (Quantile Regression Neural Network) to correct the cloud
impact in each 183\,GHz channel using measurements from all available channels
of 325\,GHz. All three options of 325\,GHz were evaluated, and the performance
was comparable. For some channels, interestingly, the spread of errors was
narrower than the noise of the target 183\,GHz channel. Another advantage of
using QRNN is that the cloud free values are predicted at different quantile
levels, which helps in quantifying the case-specific uncertainty estimate. A
similar QRNN model with 229\,GHz gave poor results. No critical dependency to
the 325\,GHz receiver noise temperature was observed.

@@

The cloud correction analysis did not give a clear value on the relative merit
of the suggested channel options and also the measurements' degree of freedom
(DoF) was assessed based on the performed simulations. The DoF can be seen as a
measure of the effective number of channels. The DoF analysis gave further
support for selecting 325\,GHz in favour of 229\,GHz. The DoF of the 325\,GHz
options is higher or equal to the 229\,GHz one, already in clear-sky conditions,
while for cloud conditions 325\,GHz consistently gives two additional degrees
of freedom. Some additional 325\,GHz channel versions were considered in the DoF
analysis.

With 325\,GHz as a better option confirmed, the next step is to establish
requirements for these channels. The study considered this question to some
extent. The cloud correction simulations gave no clear constraints on the
requirements, while the DoF analysis at least gave some indications. By
comparison to the NE$\Delta$T requirements for ICI and DoF values derived, it
is suggested to set threshold, target and breakthrough for the 325\,GHz
receiver noise temperature to 2400, 1800 and 1200\,K, respectively. Regarding
number, position and widths of channels, the differences between considered
options are relatively small and at this point, it seems reasonable to let
technical considerations guide the basic selection between having three or four
channels. Later, when the technical constraints (such as the IF range
available) are better known an updated assessment should be performed to set
the final channel values.

@@

\subsubsection{Fascod}
\label{sec:fascod}
%
The Fascod dataset \citep{anderson1986afgl} was used to represent different
climate zones in overview calculations. The dataset consists of profiles of
pressure, temperature and volume mixing ratio profiles of various atmospheric
gases. Five climatologies were used: tropical (TRO), mid-latitude summer (MLS),
mid-latitude winter (MLW), sub-arctic summer (SAS), and sub-arctic winter
(SAW). No hydrometeors were included in simulations involving Fascod.

@@

Since in this study, the cases with cloud impact are extremely important, we used ``clear-sky thinning'' to improve the representation of the cloudy cases in the dataset. Thinned dataset is a subset of the full dataset with 50\% of the clear-sky cases removed (cloud impact $<$ 0.2\,K). The size of the thinned dataset is different for each channel.

@@

A statistical comparison of the simulations to actual ATMS data, for channels
16-22 at nadir (zenith angle = $180^{\degree}$), is shown in
Fig.~\ref{fig:pdf:c16-22}. For the comparison, the daytime ATMS observations
were selected as CloudSat operates only during the day part of the orbit since
2011. For the channels around 183\,GHz, the ATMS characteristics are not fully
simulated. The ATMS channel widths are considered, but as AWS is only covering
the lower wing of the 183\,GHz transition the upper side-band of ATMS is not
included.

@@

In the intermediate region, the simulations have a lower occurrence rate. The
impact of hydrometeors should be somewhat higher in the upper side-band of ATMS,
which is not reflected in the simulations, but this is not sufficient to
explain the deviation. As this region is well covered in the simulations
reported in Fig.~7 of \citet{eriksson:towar:20}, the deviation of concern is
presumably also a consequence of the neglected antenna pattern. In this study,
this transitional region is of high interest. For this reason, the PDF for a
50\% random rejection of cases with an insignificant cloud impact is also
shown. This PDF gives a fair match in the intermediate region (but gives an
even higher over-representation at more strong cloud impacts). This smaller
dataset will be considered in parallel below, to ensure that no fraction of the
``cloudy'' cases is not under-represented in the results.

@@

\subsubsection{Training}
%  
\label{sec:qrnn:training}
\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{quantile_loss.png}
	\caption{The mean quantile loss with different configurations of layer width and hidden layers ($n_h$). Here QRNN is trained to predict clear-sky values for AWS-34 using four channels option of 325\,GHz}
	\label{fig:quantile_loss}
\end{figure}
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz
channels using TBs measurements from all available channels of 325\,GHz. A
separate QRNN is used for each of the 183\,GHz channels. For example, to
predict clear-sky TBs from AWS-34, the training data is measurements from all
channels of 325\,GHz and measurements from the 183\,GHz to be predicted. We
assess the performance of the scheme using both three channel and four channel
options of 325\,GHz. Two suggestions for three channel option are described in
Sec.~\ref{sec:channel:configurations}, and both have been used to train QRNN
separately. Thus, for each channel of 183\,GHz, we have a set of three
predictions: one from four channel option, and two from the old and new
configurations of the three channel option. Further in the text, the old and
new three channel configurations are labelled as ``three-a'' and ``three-b''.

To develop the QRNN scheme, we use the same dataset as in the
simple scheme . Out of 125\,460 simulations, 90\% are used to train the model,
while the rest 10\% is used to evaluate the model's performance during
training. Presently we train QRNN for only nadir sensor viewing angle and the
receiver noise $T_r$ = 1200\,K. In the training process, noise is added to the
input according to Eq.~\ref{eq:noise}, every time the training data are exposed
to the model. This ensures that the model is exposed to a new dataset on every
iteration. Before training, the input data is normalized with mean and standard
deviation.

@@

\subsection{Prediction accuracy}
%
We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. To analyse the prediction accuracy, a testing dataset was constructed by randomly drawing 25\,000 cases from the simulation dataset. Noise was added to each simulation to mimic a new measurement dataset.

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
		uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
		corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
		corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
		corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\
		\hline
	\end{tabular}
	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}. The labels ``three-a'', ``three-b'' correspond to the old and new suggestions of three channels options of 325\,GHz, and the label ``four'' represents the four channels option.}
	\label{tab:qrnn:C34}
\end{table}

@@

In an analogy between the results from the simple correction scheme and QRNN, we perform a similar error distribution analysis as in Sec.~\ref{sec:simple}. Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using three (three-b) and four channel options of 325\,GHz. Measurements with cases with $Tb2 - Tb1 > -15$\,K are assumed to be too-cloudy and are filtered out. Here $Tb1$ denotes TBs from AWS-34 and and $Tb2$ is the paired counterpart from 325\,GHz, i.e., AWS-42.  Both the three channels and four channels QRNN models are successful in predicting the clear-sky noise-free value for AWS-34, and the resulting error distribution is symmetric. The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}. The fraction of cases rejected as ``too-cloudy'' is also provided under ``fraction rejected''. For AWS-34, average deviation in the predictions from all three QRNN models are comparable.  The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.32), however the predictions have relatively symmetric error distributions as reflected by the low skewness values. Among the three set of predictions, option three-b has the most symmetric error distribution but with a relatively large spread. Predictions from option four have the lowest standard deviation (0.620\,K), which is interestingly smaller than the standard deviation of noise (0.641\,K). Though, all three options of 325\,GHz provide a full coverage to the hydrometer impact in AWS-34, predictions from four channel option have slightly better accuracy.

@@

To inspect if the predictions follow a normal distribution, we evaluate the
length of confidence intervals from the median.
Figure~\ref{fig:prediction_uncertainty} shows the prediction uncertainty in
AWS-34 (four channel option). The uncertainty with respect to the median for
1000 randomly selected cases is shown. The red line represents the uncertainty
in a hypothetical Gaussian distribution of $270\pm0.62$\,K. If the underlying
distribution is Gaussian, the prediction uncertainty should be symmetric around
the median, and the uncertainties should be equally spaced for $1\sigma$,
$2\sigma$ and so on. The predictions from our QRNN model seem to be symmetric
around the median for the 94\% confidence interval ($\pm 2 \sigma$). The figure
also shows that the uncertainties for all 1000 random cases are concentrated
along a narrow width, thus suggesting that the case to case variability of the
uncertainty is low. A similar uncertainty quantification for other 183\,GHz
channels also gives similar results.

@@

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise                      & -0.001 & 0.451 &              0.020 &      - \\
		uncorrected                & -1.343 & 5.908 &             -7.484 &      - \\
		corrected (AWS-4X)         &  0.008 & 1.514 &             -4.085 &      3.678 \\
		corrected (four channel)   & -0.011 & 0.878 &             -3.030 &      4.930 \\
		\hline
	\end{tabular}
	\caption{Statistics for the error distributions of AWS-32 shown in Figure~\ref{fig:qrnn_C32_C4X:deviations}. The QRNN model is trained with measurements from AWS-4X and AWS-32.}
	\label{tab:qrnn:C32:C4X}
\end{table} 
We also tested the QRNN model to predict cloud-free TBs by using measurements
from AWS-4X and AWS-32 as input. In this case, we trained QRNN with
measurements from AWS-32 and AWS-4X, to predict the clear-sky cloud free TBs
for AWS-32. The model was trained as described in
Sec.~\ref{sec:qrnn:training}, but slightly better training results were
obtained with width as 256 neurons. Other structural and training parameters
remain unchanged.

@@

\section{Sensitivity to different $T_r$}
\label{sec:tr}
%
In the previous section, we presented the results from QRNN trained using the
three suggestions of 325\,GHz proposed in
Sec.~\ref{sec:channel:configurations}. The receiver noise ($T_r$) was
assumed to be 1200\,K for all cases. In this section, we explore the
sensitivity of QRNN to a higher receiver noise. The QRNN training is repeated
for all three suggestions of 325\,GHz, but with $T_r$ = 1800\,K and $T_r$ =
2400\,K. QRNN is trained with identical structural and training parameters as
described earlier. Tables showing the statistics for error distributions for
each channel are provided. Table~\ref{tab:qrnn:C32:Trec:1800} -
Table~\ref{tab:qrnn:C36:Trec:1800} show the statistics for AWS-32, AWS-33,
AWS-34, AWS-35 and AWS-36 respectively, when $T_r$ = 1800\,K. Similarly
Table~\ref{tab:qrnn:C32:Trec:2400} - Table~\ref{tab:qrnn:C36:Trec:2400} show
the statistics when $T_r$ = 2400\,K.

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      & -0.001 & 0.451 &              0.020 &      - \\
	uncorrected                & -1.342 & 5.908 &             -7.479 &      - \\
	corrected (three-a) 	   & -0.009 & 0.893 &             -3.092 &      4.990 \\
    corrected (three-b) 	   &  0.009 & 0.888 &             -3.197 &      4.902 \\	
	corrected (four channel)   &  0.006 & 0.860 &             -2.943 &      4.954 \\
		\hline
	\end{tabular}
	\caption{Error statistics for AWS-32, when the model is trained with $T_r$ = 1800\,K. The definitions of ``three-a'', ``three-b'' and ``four'' are same as described in Table~\ref{tab:qrnn:C34} }
	\label{tab:qrnn:C32:Trec:1800}
\end{table}

@@

%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.002 & 0.454 &              0.003 &      - \\
uncorrected                 & -1.343 & 5.907 &             -7.483 &      - \\
corrected (three-a)  		& -0.017 & 0.877 &             -3.381 &      4.934 \\
corrected (three-b)  		& -0.015 & 0.882 &             -3.177 &      4.974 \\
corrected (four channel)    &  0.028 & 0.876 &             -3.638 &      4.978 \\
		\hline
	\end{tabular}
	\caption{ Error statistics for AWS-32, when the model is trained with $T_r$ = 2400\,K. The definitions of ``three-a'', ``three-b'' and ``four'' are same as described in Table~\ref{tab:qrnn:C34}  }
	\label{tab:qrnn:C32:Trec:2400}
\end{table}

@@

As an example, Fig~\ref{fig:DoF:clear:1200K} shows the ratio of
$\Lambda/S_\Lambda$ with respect to the eigenvalue index for clear-sky cases.
The DoF in the section below, is an interpolation between the last index having a ratio above
one and next index.

@@

At this point we got a feedback from Omnisys that also channel option three-b is
technically challenging. In short, it is significantly more difficult to
implement a 3\,GHz wide channel at an IF of 3.3\,GHz (AWS-42) than compared to
at 6.5\,GHz (AWS-41). To decrease the ratio between channel widths and centre
IF, a third three channel option was formulated (Table~\ref{tab:chs:3c}) that
is below denoted as three-c. This option uses the same IF range as the
previously suggested ones.

@@

\subsection{Impact of extending the IF range}
%
As a basic investigation of the impact of changing the width of the IF range, a
version of the four channel option was considered, denoted as four-b. It was
modified to cover 0.7 to 9.0 GHz (instead of 0.7 to 8.0 GHz). To focus on the
extension, only the edge channels were changed. That is, the revised AWS-41 and AWS-44
have bandwidth of 3.8 and 0.9\,GHz, respectively. The DoFs obtained for four-b
are found in Table~\ref{tab:DoF:4b}.

As expected a slight improvement of the DoF can be seen for four-b. The
exception ``all'' and $T_r=2400$\,K, again is likely an indication on some noise
in the DoFs coming out of the analysis.

The results indicate that a broader IF range should give slightly better performance. If a broader IF range is feasible, the position and width of all channels should be revised, but this is out of the scope of this study, and anyhow hardly motivated before it is known more exactly to what extent the IF range can be extended.

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
      &	325\,GHz & \multicolumn{3}{c}{DoF}   \\
      &	option &  $T_r = 1200 $\,K &   $T_r = 1800 $\,K &   $T_r = 2400$\,K \\
      \hline
      all &	four   &              8.2 &              7.8 &              6.2 \\
      & four-b   &              8.3 &              8.0   &              6.1 \\

      \hline
      clear  &	four  &                7.0 &              6.0 &              4.9 \\
      &   four-b &                7.0 &              6.4 &              4.9 \\

      \hline	
      cloudy &	four  &              8.7 &              8.5 &              8.3 \\
      &   four-b &              8.8 &              8.6 &              8.4 \\
      \hline
\end{tabular}
\caption{The degrees of freedom for channel option four-b. Values for option
  four are repeated from Tables~\ref{tab:DoF:all}-\ref{tab:DoF:clear}. }
\label{tab:DoF:4b}
\end{table}
\section{Discussion}

@@

\subsubsection{Performance of QRNN}
In Sec.~\ref{sec:qrnn} we use QRNN as a method for cloud correction based on
325\,GHz data. Measurements from all 325\,GHz channels and the 183\,GHz channel
to be predicted are used to train the QRNN model.

@@

For AWS-32, the QRNN trained with 325\,GHz is only partially successful in
reducing the impact of hydrometeors. The resulting error distributions have
significantly lower spread than the measurements, but are still negatively
skewed. Among the three combinations of 325\,GHz, the four channel option has
slightly better performance. Since 325\,GHz cannot provide a full coverage for
hydrometeor impact in AWS-32, QRNN cannot learn to predict cloud free values
for instances which lie outside the area of coverage. In order to compare the
229\,GHz channel with 325\,GHz, QRNN was also trained with AWS-4X to predict
cloud free AWS-32. The performance of QRNN trained with AWS-4X is worse
than training with 325\,GHz. The spread of error distributions is 1.5 times
more than obtained with four channels option of 325\,GHz.
